---
title: 'Homework 3'
author: "Dhruv Dole"
date: "2/17/2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
```

#### Due: 2/17/2023 before 11:59pm. Submit in Canvas (file upload).

1. Finish the in-class practice in Slides 3-12 in "Lecture 2-2-Practice for git", link: https://yumouqiu.github.io/DS202-Spring2023/Practice/practice01.html  
a. Download the RMarkdown file with these homework instructions to use as a template for your work. Make sure to replace "Your Name" with your name.
b. In the RMarkdown file, write down table of team members, and their github repository links;
the number of successful pull requests you made, and the github repository to which you requested a change;  
the number of pull requests you accepted, and the github repository from which you accepted.

| member | repo                          | # of PRs made                         | # of Prs accepted |
|--------|-------------------------------|---------------------------------------|-------------------|
| Dhruv  | dsdole/practice1-your-gitname | **1** @ dsdole/AGHW3                  | **?**             |
| Ahmed  | bobagh/AGHW3                  | **?** @ bobagh/practice1-your-gitname | **?**             |


    c. Write down a list with at least 3 tips of how to make working with git/github easier  
        1. Commit frequently and cleanly.
        2. Pull remote changes frequently.
        3. Commit messages should be consice and informative.
2. Generate the graph of LifExp vs. gdpPercap for US, Canada (fixed data) and Australia by RMarkdown based on the data set "gapminder-5060", like what we did in the class.  
Please use Github to collaborate on this problem. For example, one member can create the plot of US in his/her repository. The other member will fork this repository, add the result for the second country, and make a pull request for merging into the main repository. Each member should at least analyze one country and make at least one pull request. **Please submit the RMarkdown file, the output file, and the screen shot of the successful pull request and the merge.**
```{r}
data <- read.csv("https://raw.githubusercontent.com/dsdole/practice1-your-gitname/300ee57bd22a06f2726855df4098032666f3fdb7/gapminder-5060.csv")
US <- data %>% filter(country == "United States")
ggplot(data = US, aes(x = year, y = lifeExp)) + geom_line()

```
3. Write a paragraph (~200 words) describing an example of what you consider data science. Write your paragraph in R Markdown. Include at least

Data science is the study of data. Its purpose is to extract insights for business. It involves many fields, including
but not limited to math, statistics, and computer science. An example of this would be an end to end data pipeline for
stock market decision making. We start first with data collection. Using various APIs we can pull data for as many
sources as needed, unstructured or not. These can be cleaned and passed into a datalake to be crawled at will. After
that data scientists can use a query engine to select data features with which they can run experimental data analytics.
The next step is creating a designing, training, and testing a statistical model to predict something. After that, a
machine learning engineer can productionalize the model and buisness leaders and stakeholders can use the model through
dashboards to view results

a. one link to a chart or an image and


b. at least one itemized or enumerated list.


Note: your submission is supposed to be fully reproducible, i.e. the TA and I will 'knit' your submission in RStudio. Including the link to the image is the tricky part here. Make sure that you don't use any file structure that depends on your computing environment.


For the submission: submit your solution in an **R Markdown file** and (just for insurance) submit the corresponding html (or Word) file with it. 
